Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-09-19 paper/paper.tex
wrote description of the pill correlation plot Tested everything on quipu.

\fixme{add explanation of correlation function somewhere in the
  following paragraph.  The math could go in theory/methods section.}
{
  \color{red}
  \begin{equation}
    C(\tau) = \frac{\int
      (N_{\textit{top}}(t) - \bar N_{\textit{top}})
      (N_{\textit{bottom}}(t+\tau) - \bar N_{\textit{bottom}})dt
    }{
      \int
      (N_{\textit{top}}(t) - \bar N_{\textit{top}})
      (N_{\textit{bottom}}(t) - \bar N_{\textit{bottom}})dt
    }
  \end{equation}
  \begin{equation}
    C(\tau) \propto \int
      (N_{\textit{top}}(t) - \bar N_{\textit{top}})
      (N_{\textit{bottom}}(t+\tau) - \bar N_{\textit{bottom}})dt
  \end{equation}
  where...
  \begin{equation}
    C(\tau) = -\cos\left(\frac{2\pi\tau}{T}\right) e^{-\frac{\tau}{\tau_0}}
  \end{equation}
  where $T$ is the period and $\tau_0$ is the coherence time.
}

We present simulations of a cell with radius $.5\micron$ and length
$4\micron$, measured from the tip of one end cap to the tip of the
other. We observe in the deterministic model a quick establishement
(within a few periods) of regular oscillatory behavoir that lasts
indefinitely.  This temporal regularity can be seen in
Figure~\ref{corr-pill}, which shows the temporal correlation of the
total MinD protein located in the the two polar sections of the cell.
In the case of the stochastic model the pill exhibits coherence times
of over 7 periods and in the case of the determinisitic model
oscillate indefinately with complete coherence.

While the stochastic results show periods that seem to have a high
degree of regularity as well as similarity to the deterministic
results, they do differ in the precise locations of the maxima.  While
the deterministic model shows maxima that are every time
concentrated in the center of one of the cell ends, with a symmetric
smear of protein going out laterally to either side, the stochastic
model shows maxima that, while always located somehwere in the polar
region of the cell, occur at different positions within this region.
This is reflected in Figure~\ref{image-p}, which shows periods that
are the same and qualitative behavoir that is approximately the same,
but also that there is variation in the details of the stochastic
model maxima location.  \fixme{I think we should discuss stochastic
  picture earlier.}

>>>>

\fixme{add explanation of correlation function somewhere in the
  following paragraph.  The math could go in theory/methods section.}
{
  \color{red}
  \begin{equation}
    C(\tau) \propto \int
      (N_{\textit{top}}(t) - \bar N_{\textit{top}})
      (N_{\textit{bottom}}(t+\tau) - \bar N_{\textit{bottom}})dt
  \end{equation}
  where...
  \begin{equation}
    C(\tau) = -\cos\left(\frac{2\pi\tau}{T}\right) e^{-\frac{\tau}{\tau_0}}
  \end{equation}
  where $T$ is the period and $\tau_0$ is the coherence time.
}

Figure~\ref{corr-pill} shows a plot of the time correlation between
the total MinD found in the two opposite polar regions.  This
normalized value is given by
\begin{equation}
  C(\tau) = \frac{\int
    (N_{\textit{top}}(t) - \bar N_{\textit{top}})
    (N_{\textit{bottom}}(t+\tau) - \bar N_{\textit{bottom}})dt
  }{
    \int
    (N_{\textit{top}}(t) - \bar N_{\textit{top}})
    (N_{\textit{bottom}}(t) - \bar N_{\textit{bottom}})dt
  }
\end{equation}
where $N_{\textit{top}}(t)$ and $N_{\textit{bottom}}(t)$ are the total
MinD proteins in the outer sections of a cell that has been divided
into thirds along its long axis.  These plots heolp us in studying the
periods and the regularity and stability of oscillations.  We have
fitted them to a simple exponential decay model (akin to that of
monochromatic light), given by the equation
\begin{equation}
  C(\tau) = -\cos\left(\frac{2\pi\tau}{T}\right) e^{-\frac{\tau}{\tau_0}}
\end{equation}
where $T$ is the period and $\tau_0$ is the coherence time.  In the
case of the stochastic model the pill exhibits coherence times of over
7 periods and in the case of the determinisitic model oscillate
indefinately with complete coherence.

\fixme{Do we want anything from the following paragrph?}While the
stochastic results show periods that seem to have a high degree of
regularity as well as similarity to the deterministic results, they do
differ in the precise locations of the maxima.  While the
deterministic model shows maxima that are every time concentrated in
the center of one of the cell ends, with a symmetric smear of protein
going out laterally to either side, the stochastic model shows maxima
that, while always located somehwere in the polar region of the cell,
occur at different positions within this region.  This is reflected in
Figure~\ref{image-p}, which shows periods that are the same and
qualitative behavoir that is approximately the same, but also that
there is variation in the details of the stochastic model maxima
location.  \fixme{I think we should discuss stochastic picture
  earlier.}
